
\title{DIP Project Proposal}
\author{Pratik Kamble}

\begin{document}

\maketitle


\section{Technical details}\label{technical-details}

\begin{itemize}
\tightlist
\item
  Project ID: \textbf{40}
\item
  Project title: \emph{Computationally efficient image deblurring using
  low rank image approximation and its GPU implementation}
\item
  Original Paper:
  \href{https://link.springer.com/content/pdf/10.1007\%2Fs11554-015-0539-x.pdf}{Chang
  et. al}
\item
  Project topics: Deblurring and GPU Implementation
\item
  Team Members:
\item
  Pratik Kamble (\textbf{20161135})
\item
  GitHub Link:
  \href{https://github.com/Pk13055/low-rank-deblurring}{low-rank-deblurring}
\end{itemize}

\section{Overview}\label{overview}

\begin{itemize}
\tightlist
\item
  This project essentially covers a computationally efficient technique
  for reduction of blur caused by handshakes in images captured by
  mobile devices. This technique uses a short-exposure or a low-exposure
  image that is captured at the same time a normal or auto-exposure
  image is captured.
\item
  The short-exposure image is enhanced by utilizing low rank image
  approximation of the auto-exposure image without requiring any user
  specified parameters.
\item
  Based on the three quantitative measures of image quality, it is shown
  that this technique outperforms similar techniques used for image
  deblurring while it also offers computational efficiency. A GPU
  implementation of this technique is also reported.
\item
  If constraints permit, a comparison between the methods mentioned in
  the paper and naive deblurring methods may also be presented.
\end{itemize}

\section{Timeline}\label{timeline}

\begin{longtable}[]{@{}cc@{}}
\toprule
Date & Task\tabularnewline
\midrule
\endhead
\textbf{Sept 29th} & \textbf{Proposal Submission}\tabularnewline
Oct (first week) & Read through paper and setup testing and
analysis\tabularnewline
\emph{Oct (second week)} & \emph{Exams}\tabularnewline
Oct (third week) & Collect additional deblurring method
data\tabularnewline
Oct (last week) & Implement efficient low rank algorithm and
test\tabularnewline
\textbf{Nov 10th} & \textbf{Midway checkpoint}\tabularnewline
Nov (last week) & Extend to GPU implementation\tabularnewline
\textbf{Nov 29th} & \textbf{Project Presentation}\tabularnewline
\bottomrule
\end{longtable}

\section{End goals}\label{end-goals}

\begin{itemize}
\tightlist
\item
  Compare and analyze the efficiency and differences in output of
  various deblurring techniques
\item
  Present and expand \emph{low rank image approximation}
\item
  Attempt a GPU implementation and compare perfomance gains.
\end{itemize}

\end{document}